What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Improve

\todo{Show also an example with \c{substitute}}

@@

\todo{There is an example in package comprenhr that does code generation with substitute to create list comprehensions, but it is quite difficult to grasp.}

>>>>

@@

\todo{There is an example in package comprenhr that does code generation with substitute to create list comprehensions, but it is quite difficult to grasp. But at the same type, we lack here an example of code generation using quite, enquote or substitute.}
